Should I Airbnb My Property: Analytic Code Explanation

### 2017-10-25 abbDataAnalysis_Script.Rmd
adding output for shiny example
fix writeout options

@@

    data.path <- 'alternate data path'
    code.path <- 'alternate data path'
    fig.path <- 'alternate data path'

  offline <- TRUE

@@

  load(paste0(data.path, 'prepared/prep_workspace.RData'))

@@

  str.data$cpppd <- 4.5
  str.data$avg.guests <- str.data$bedrooms * 1.5

@@

  str.data$str.obs.revenue <- ((str.data$bookings * str.data$med.rate) - 
                                 (str.data$bookings * str.data$avg.guests *
                                    str.data$cpppd))

@@

  str.data$extr.par <- 366 / str.data$total.days

  str.data$str.act.revenue <- ((str.data$bookings * str.data$extr.par *
                                  str.data$med.rate) - 
                                 (str.data$bookings * str.data$avg.guests * 
                                    str.data$cpppd * str.data$extr.par))
```

@@

  str.data$occ.rate <- 1 - (str.data$block.rate + str.data$avail.rate)

  str.data$pot.occ.rate <- ((str.data$bookings * str.data$extr.par) / 
    (366 - (366 * str.data$block.rate)))

  str.data$str.pot.revenue <- ((str.data$pot.occ.rate * 366 * str.data$med.rate) - 
                                 (str.data$pot.occ.rate * 366 * 
                                    str.data$avg.guests * str.data$cpppd))

@@

  imp.data <- imputeLtrRents(ltr.df=ltr.data,
                               str.df=str.data,
                               mod.spec=ltr.mod.spec,
                               match.factor='suburb')

@@

  # Extract out DFs (only those that imputed)
  str.metro <- merge(str.data, imp.data$imp.rent, by='property.id')

@@

The above process of long-term revenue estimation treated the entire market as operating similarly. Realizing that the imputed long term rental values and search times may be more accurate when estimated at smaller scales, we functionalize the above processes and then apply it to short-term rentals, broken into submarkets by type, bed/bath and geographic area.  In other words, we separately estimate LTR rents for Apartments with 1bed/1bath in the city core, Apartments with 1bed/1bath in the beach submarket, etc. for all compbinations of type, bed/bath and geographic area. We then combine the results form all estimates back into a single data.frame that contains all of the short-term rentals. We use these finer scale estimates going forward (the data in the **str.data.ic** object).

@@

 str.data$tbg <- paste0(str.data$product,'.', str.data$geo.mrkt)
 ltr.data$tbg <- paste0(ltr.data$product,'.', ltr.data$geo.mrkt)

@@

 str.data.ic <- abbImputeCompare(str.df=str.data,
                                 ltr.df=ltr.data,
                                 mod.spec=ltr.mod.spec,
                                 match.factor='suburb',
                                 split.field='tbg',
                                 verbose=FALSE)

@@

  # Actual
   stra.rev <- str.data.ic[,c('property.id', 'str.act.revenue')]
   stra.rev$tenure <- 'Short-Term (Actual)   '
   names(stra.rev)[2] <- 'revenue'

  # Potential
   strp.rev <- str.data.ic[,c('property.id', 'str.pot.revenue')]
   strp.rev$tenure <- 'Short-Term (Potential)   '
   names(strp.rev)[2] <- 'revenue'

  # Long-Term
   ltr.rev <- str.data.ic[,c('property.id', 'ltr.imp.revenue')]
   ltr.rev$tenure <- 'Long-Term   '
   names(ltr.rev)[2] <- 'revenue'

@@

  table(str.data.ic$str.act.pref) / nrow(str.data.ic)

@@

  str.data.ic$pref <- str.data.ic$str.act.pref

@@

  str.data.ic$occ.qtl <- makeWtdQtl(str.data.ic$occ.rate, 
                                      return.type='rank') 
  str.data.ic$rate.qtl <- makeWtdQtl(str.data.ic$med.rate, 
                                  return.type='rank')

@@

  rawocc.metro <- abbPrefPlot(str.data.ic,
                         x.field='occ.rate',
                         smooth=TRUE,
                         smooth.span=.5)

  qtlocc.metro <- abbPrefPlot(str.data.ic,
                        x.field='occ.qtl',
                        smooth=TRUE,
                        smooth.span=.5)

@@

  rate.hm <- abbHeatMap(str.data.ic,
                x.field='occ.rate',
                y.field='med.rate',
                pref.field='str.act.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm + ylab('Nightly Rate')

@@

  rate.hm.svm <- abbHeatMap(str.data.ic,
                            x.field='occ.rate',
                            y.field='med.rate',
                            pref.field='str.act.pref',
                            svm=T, 
                            alpha.count=F,
                            add.points=T,
                            fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm.svm+ ylab('Nightly Rate')

@@

  qtl.hm <- abbHeatMap(str.data.ic,
                x.field='occ.qtl',
                y.field='rate.qtl',
                pref.field='str.act.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  qtl.hm+ ylab('Nightly  (Pcntl)')

@@

  qtl.hm.svm <- abbHeatMap(str.data.ic,
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T, 
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))
  qtl.hm.svm+ ylab('Nightly  (Pcntl)')

@@

 # Make Basic comparison table
  pref.table.type <- abbCreateCompTable(ic.df=str.data.ic,
                                   split.field='type')

@@

  type.data.ic <- str.data.ic

  # Id the types
  apt.id <- which(str.data.ic$type == 'Apartment')
  house.id <- which(str.data.ic$type == 'House')

@@

  subm.data.ic <- str.data.ic

  # Get IDs
  cc.id <- which(str.data.ic$geo.mrkt == 'city-core')
  city.id <- which(str.data.ic$geo.mrkt == 'city')
  sub.id <- which(str.data.ic$geo.mrkt == 'suburban')
  rural.id <- which(str.data.ic$geo.mrkt == 'rural')
  beach.id <- which(str.data.ic$geo.mrkt == 'beach')

@@

  str.data.ic$bedbath <- factor(str.data.ic$bedbath,
                                levels=c('1..1', '2..1', '2..2',
                                         '3..1', '3..2', '4..2'))

  mod.act.str <- glm(str.act.pref~type+as.factor(bedbath),
                     family=binomial(link='logit'),
                     data=str.data.ic)
  mod.pot.str <- glm(str.pot.pref~type+as.factor(bedbath),
                     family=binomial(link='logit'),
                     data=str.data.ic)
```

@@

  mod.act.loc <- glm(str.act.pref~type+as.factor(bedbath)+
                                  geo.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)
  mod.pot.loc <- glm(str.pot.pref~type+as.factor(bedbath)+
                                  geo.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)
```

@@

  mod.act.host <- glm(str.act.pref~type+as.factor(bedbath)+
                        geo.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
                        geo.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
```

@@

  mod.act.str.prem <- lm(str.act.prem~type+as.factor(bedbath),
                    data=str.data.ic)
  mod.pot.str.prem <- lm(str.pot.prem~type+as.factor(bedbath),
                    data=str.data.ic)

  mod.act.loc.prem <- glm(str.act.pref~type+as.factor(bedbath)+
                                  geo.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)
  mod.pot.loc.prem <- glm(str.pot.pref~type+as.factor(bedbath)+
                                  geo.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)

  mod.act.host.prem <- lm(str.act.prem~type+as.factor(bedbath)+
                        geo.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str.data.ic)
  mod.pot.host.prem <- lm(str.pot.prem~type+as.factor(bedbath)+
                        geo.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str.data.ic)
```

@@

  pot.data.ic <- str.data.ic

@@

  host.block.freq <- ggplot(str.data, aes(x=block.rate)) + 
  geom_density(fill=str.col, color=str.col) +
  ylab('Frequency\n') + 
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0,1,.2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    ggtitle('Host Block Rate Frequency\n') +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.text.y=element_blank(),
          axis.ticks.y=element_blank())

@@

  block.rate.period <- ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
  geom_point(fill=str.col, color=str.col, size=.2) +
  ylab('Nbr of Blocked Periods\n') + 
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0, 1, .2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

str.data.ic$blockpertime <- round(str.data.ic$nbr.block * str.data.ic$extr.par, 1)

str.data.ic$host.type <- 'Unknown'
str.data.ic$host.type[str.data.ic$blockpertime > 12] <- 'Multi-Platform User'
str.data.ic$host.type[str.data.ic$block.rate <= .25] <- 'Profit Seeker'
str.data.ic$host.type[str.data.ic$block.rate >= .75] <- 'Opportunistic Sharer'
str.data.ic$host.type <- factor(str.data.ic$host.type,
                             levels=c('Profit Seeker', 'Opportunistic Sharer', 
                                      'Multi-Platform User', 'Unknown'))

host.type <- ggplot(str.data.ic, 
       aes(x=block.rate, y=blockpertime, color=host.type)) + 
  geom_point(alpha=.5, size=.8, shape=16) +
  ylab('Number of Blocked Periods\n') + 
  xlab('\n% of Time Property is Blocked') +
      ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +

@@

host.type.bar <- ggplot(str.data.ic, aes(host.type, fill=host.type)) +
  geom_bar() +
  scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
  theme(legend.position='none') +
  ylab('Frequency\n') + 
  xlab('\nHost Type') +
  ggtitle('Short Term Host Types') + 
  theme(plot.title = element_text(hjust = 0.5))

@@

  ps <- which(str.data.ic$host.type == 'Profit Seeker')
  os <- which(str.data.ic$host.type == 'Opportunistic Sharer')
  mu <- which(str.data.ic$host.type == 'Multi-Platform User')
  un <- which(str.data.ic$host.type == 'Unknown')

  mod.pot.ps <- glm(str.pot.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[ps,])

  mod.pot.os <- glm(str.pot.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[os,])

  mod.pot.mu <- glm(str.pot.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[mu,])

  mod.pot.un <- glm(str.pot.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[un,])

  mod.act.ps <- glm(str.act.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[ps,])

  mod.act.os <- glm(str.act.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[os,])

  mod.act.mu <- glm(str.act.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[mu,])

  mod.act.un <- glm(str.act.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[un,])

@@

save(clean.count, daily.data, listing.data, ltr.data, pref.table,
     pref.table.wide, revdens.data, rawocc.metro, qtlocc.metro, rawocc.type,
     pctocc.type, subm.data.ic, rawocc.geo, pctocc.geo, type.data.ic, pot.data.ic,
     str.data, str.data.ic, subs,
     core.suburbs,  exch.rate, host.models, pref.models, prem.models,
     file=paste0(data.path, 'analyzed/analyzed_workspace.RData'))

@@

<!--  ssubs <- table(str.data.ic$suburb) -->
<!--  s.subs <- subs[subs$id %in% names(ssubs),] -->
<!--  s.suburbs <- suburbs.shp[suburbs.shp@data$NAME_2006 %in% names(ssubs),] -->
<!--  sssubs <- fortify(s.suburbs) -->

@@

<!--  # Create estimation points -->
<!--  est.data <- str.data.ic -->
<!--  est.points <- createGridPoints(s.suburbs, scale, T) -->

>>>>

```{r set_dates}

  data_name <- 'jun'
  strike_date <- lubridate::as_date('2015-06-01')

@@

@@

  load(file.path(data.path, 'prepared', paste0('prep_workspace_', data_name, '.RData')))

@@

  str_df$cpppd <- 4.5
  str_df$avg.guests <- str_df$bedrooms * 1.5

@@

  str_df$str.obs.revenue <- ((str_df$bookings * str_df$med.rate) - 
                                 (str_df$bookings * str_df$avg.guests *
                                    str_df$cpppd))

@@

  str_df$extr.par <- 366 / str_df$total.days

  str_df$str.act.revenue <- ((str_df$bookings * str_df$extr.par *
                                  str_df$med.rate) - 
                                 (str_df$bookings * str_df$avg.guests * 
                                    str_df$cpppd * str_df$extr.par))
```

@@

  str_df$occ.rate <- 1 - (str_df$block.rate + str_df$avail.rate)

  str_df$pot.occ.rate <- ((str_df$bookings * str_df$extr.par) / 
    (366 - (366 * str_df$block.rate)))

  str_df$str.pot.revenue <- ((str_df$pot.occ.rate * 366 * str_df$med.rate) - 
                                 (str_df$pot.occ.rate * 366 * 
                                    str_df$avg.guests * str_df$cpppd))

@@

  imp.data <- imputeLtrRents(ltr.df=ltr.data,
                               str.df=str_df,
                               mod.spec=ltr.mod.spec,
                               match.factor='suburb')

@@

  # Extract out DFs (only those that imputed)
  str.metro <- merge(str_df, imp.data$imp.rent, by='property.id')

@@

The above process of long-term revenue estimation treated the entire market as operating similarly. Realizing that the imputed long term rental values and search times may be more accurate when estimated at smaller scales, we functionalize the above processes and then apply it to short-term rentals, broken into submarkets by type, bed/bath and geographic area.  In other words, we separately estimate LTR rents for Apartments with 1bed/1bath in the city core, Apartments with 1bed/1bath in the beach submarket, etc. for all compbinations of type, bed/bath and geographic area. We then combine the results form all estimates back into a single data.frame that contains all of the short-term rentals. We use these finer scale estimates going forward (the data in the **str_df.ic** object).

@@

 str_df$tbg <- paste0(str_df$product,'.', str_df$geo.mrkt)
 ltr.data$tbg <- paste0(ltr.data$product,'.', ltr.data$geo.mrkt)

@@

 str_df.ic <- abbImputeCompare(str.df=str_df,
                                 ltr.df=ltr.data,
                                 mod.spec=ltr.mod.spec,
                                 match.factor='suburb',
                                 split.field='tbg',
                                 verbose=FALSE)

@@

  # Actual
   stra.rev <- str_df.ic[,c('property.id', 'str.act.revenue')]
   stra.rev$tenure <- 'Short-Term (Actual)   '
   names(stra.rev)[2] <- 'revenue'

  # Potential
   strp.rev <- str_df.ic[,c('property.id', 'str.pot.revenue')]
   strp.rev$tenure <- 'Short-Term (Potential)   '
   names(strp.rev)[2] <- 'revenue'

  # Long-Term
   ltr.rev <- str_df.ic[,c('property.id', 'ltr.imp.revenue')]
   ltr.rev$tenure <- 'Long-Term   '
   names(ltr.rev)[2] <- 'revenue'

@@

  table(str_df.ic$str.act.pref) / nrow(str_df.ic)

@@

  str_df.ic$pref <- str_df.ic$str.act.pref

@@

  str_df.ic$occ.qtl <- makeWtdQtl(str_df.ic$occ.rate, 
                                      return.type='rank') 
  str_df.ic$rate.qtl <- makeWtdQtl(str_df.ic$med.rate, 
                                  return.type='rank')

@@

  rawocc.metro <- abbPrefPlot(str_df.ic,
                         x.field='occ.rate',
                         smooth=TRUE,
                         smooth.span=.5)

  qtlocc.metro <- abbPrefPlot(str_df.ic,
                        x.field='occ.qtl',
                        smooth=TRUE,
                        smooth.span=.5)

@@

  rate.hm <- abbHeatMap(str_df.ic,
                x.field='occ.rate',
                y.field='med.rate',
                pref.field='str.act.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm + ylab('Nightly Rate')

@@

  rate.hm.svm <- abbHeatMap(str_df.ic,
                            x.field='occ.rate',
                            y.field='med.rate',
                            pref.field='str.act.pref',
                            svm=T, 
                            alpha.count=F,
                            add.points=T,
                            fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm.svm+ ylab('Nightly Rate')

@@

  qtl.hm <- abbHeatMap(str_df.ic,
                x.field='occ.qtl',
                y.field='rate.qtl',
                pref.field='str.act.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  qtl.hm+ ylab('Nightly  (Pcntl)')

@@

  qtl.hm.svm <- abbHeatMap(str_df.ic,
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T, 
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))
  qtl.hm.svm+ ylab('Nightly  (Pcntl)')

@@

 # Make Basic comparison table
  pref.table.type <- abbCreateCompTable(ic.df=str_df.ic,
                                   split.field='type')

@@

  type.data.ic <- str_df.ic

  # Id the types
  apt.id <- which(str_df.ic$type == 'Apartment')
  house.id <- which(str_df.ic$type == 'House')

@@

  subm.data.ic <- str_df.ic

  # Get IDs
  cc.id <- which(str_df.ic$geo.mrkt == 'city-core')
  city.id <- which(str_df.ic$geo.mrkt == 'city')
  sub.id <- which(str_df.ic$geo.mrkt == 'suburban')
  rural.id <- which(str_df.ic$geo.mrkt == 'rural')
  beach.id <- which(str_df.ic$geo.mrkt == 'beach')

@@

  str_df.ic$bedbath <- factor(str_df.ic$bedbath,
                                levels=c('1..1', '2..1', '2..2',
                                         '3..1', '3..2', '4..2'))

  mod.act.str <- glm(str.act.pref~type+as.factor(bedbath),
                     family=binomial(link='logit'),
                     data=str_df.ic)
  mod.pot.str <- glm(str.pot.pref~type+as.factor(bedbath),
                     family=binomial(link='logit'),
                     data=str_df.ic)
```

@@

  mod.act.loc <- glm(str.act.pref~type+as.factor(bedbath)+
                                  geo.mrkt,
                     family=binomial(link='logit'),
                     data=str_df.ic)
  mod.pot.loc <- glm(str.pot.pref~type+as.factor(bedbath)+
                                  geo.mrkt,
                     family=binomial(link='logit'),
                     data=str_df.ic)
```

@@

  mod.act.host <- glm(str.act.pref~type+as.factor(bedbath)+
                        geo.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str_df.ic)
  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
                        geo.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str_df.ic)
```

@@

  mod.act.str.prem <- lm(str.act.prem~type+as.factor(bedbath),
                    data=str_df.ic)
  mod.pot.str.prem <- lm(str.pot.prem~type+as.factor(bedbath),
                    data=str_df.ic)

  mod.act.loc.prem <- glm(str.act.pref~type+as.factor(bedbath)+
                                  geo.mrkt,
                     family=binomial(link='logit'),
                     data=str_df.ic)
  mod.pot.loc.prem <- glm(str.pot.pref~type+as.factor(bedbath)+
                                  geo.mrkt,
                     family=binomial(link='logit'),
                     data=str_df.ic)

  mod.act.host.prem <- lm(str.act.prem~type+as.factor(bedbath)+
                        geo.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str_df.ic)
  mod.pot.host.prem <- lm(str.pot.prem~type+as.factor(bedbath)+
                        geo.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str_df.ic)
```

@@

  pot.data.ic <- str_df.ic

@@

  host.block.freq <- ggplot(str_df, aes(x=block.rate)) + 
  geom_density(fill=str.col, color=str.col) +
  ylab('Frequency\n') + 
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0,1,.2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    ggtitle('Host Block Rate Frequency\n') +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.text.y=element_blank(),
          axis.ticks.y=element_blank())

@@

  block.rate.period <- ggplot(str_df, aes(x=block.rate, y=nbr.block*extr.par)) + 
  geom_point(fill=str.col, color=str.col, size=.2) +
  ylab('Nbr of Blocked Periods\n') + 
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0, 1, .2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

str_df.ic$blockpertime <- round(str_df.ic$nbr.block * str_df.ic$extr.par, 1)

str_df.ic$host.type <- 'Unknown'
str_df.ic$host.type[str_df.ic$blockpertime > 12] <- 'Multi-Platform User'
str_df.ic$host.type[str_df.ic$block.rate <= .25] <- 'Profit Seeker'
str_df.ic$host.type[str_df.ic$block.rate >= .75] <- 'Opportunistic Sharer'
str_df.ic$host.type <- factor(str_df.ic$host.type,
                             levels=c('Profit Seeker', 'Opportunistic Sharer', 
                                      'Multi-Platform User', 'Unknown'))

host.type <- ggplot(str_df.ic, 
       aes(x=block.rate, y=blockpertime, color=host.type)) + 
  geom_point(alpha=.5, size=.8, shape=16) +
  ylab('Number of Blocked Periods\n') + 
  xlab('\n% of Time Property is Blocked') +
      ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +

@@

host.type.bar <- ggplot(str_df.ic, aes(host.type, fill=host.type)) +
  geom_bar() +
  scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
  theme(legend.position='none') +
  ylab('Frequency\n') + 
  xlab('\nHost Type') +
  ggtitle('Short Term Host Types') + 
  theme(plot.title = element_text(hjust = 0.5))

@@

  ps <- which(str_df.ic$host.type == 'Profit Seeker')
  os <- which(str_df.ic$host.type == 'Opportunistic Sharer')
  mu <- which(str_df.ic$host.type == 'Multi-Platform User')
  un <- which(str_df.ic$host.type == 'Unknown')

  mod.pot.ps <- glm(str.pot.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str_df.ic[ps,])

  mod.pot.os <- glm(str.pot.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str_df.ic[os,])

  mod.pot.mu <- glm(str.pot.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str_df.ic[mu,])

  mod.pot.un <- glm(str.pot.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str_df.ic[un,])

  mod.act.ps <- glm(str.act.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str_df.ic[ps,])

  mod.act.os <- glm(str.act.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str_df.ic[os,])

  mod.act.mu <- glm(str.act.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str_df.ic[mu,])

  mod.act.un <- glm(str.act.pref~type+as.factor(bedbath)+
                    geo.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str_df.ic[un,])

@@

  save(clean.count, daily_df, listing.data, ltr.data, pref.table,
       pref.table.wide, revdens.data, rawocc.metro, qtlocc.metro, rawocc.type,
       pctocc.type, subm.data.ic, rawocc.geo, pctocc.geo, type.data.ic, pot.data.ic,
       str_df, str_df.ic, subs,
       core.suburbs,  exch.rate, host.models, pref.models, prem.models,
       file=file.path(data.path, 'analyzed', paste0('analyzed_workspace_', data_name, 
                                                    '.RData')))

  save(str_df.ic, subs, abb.col, file=file.path(data.path,'analyzed', 
                                                paste0('shinyinput_', data_name, 
                                                       '.RData')))

@@

<!--  ssubs <- table(str_df.ic$suburb) -->
<!--  s.subs <- subs[subs$id %in% names(ssubs),] -->
<!--  s.suburbs <- suburbs.shp[suburbs.shp@data$NAME_2006 %in% names(ssubs),] -->
<!--  sssubs <- fortify(s.suburbs) -->

@@

<!--  # Create estimation points -->
<!--  est.data <- str_df.ic -->
<!--  est.points <- createGridPoints(s.suburbs, scale, T) -->
